
\documentclass[]{awesome-cv}
\usepackage{textcomp}
\fontdir[fonts/]
\newcommand*{\sectiondir}{resume/}
\colorlet{awesome}{awesome-red}
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	\headerfirstnamestyle{Abhay} \headerlastnamestyle{Khera} \\
	\vspace{2mm}
	{\faEnvelope\ abhaykhera18@gmail.com} | {\faMobile\ 7358527090} | {\faMapMarker\ Chennai TN} | {\faLink\ https://www.linkedin.com/in/abhaykhera/}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Education}
\begin{cventries}
	\cventry
	{B.Tech in Computer Science and Engineering}
	{VIT University}
	{Chennai , TN}
	{2015 – 2019}
	{GPA: 8.58}
	\cventry
	{Senior Secondary in Science}
	{Ryan International School}
	{Ludhiana , PB}
	{2013 – 2015}
	{GPA: 84\%}
\end{cventries}

\vspace{-2mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Experience}
\begin{cventries}
	\cventry
	{QA Intern}
	{Dataguise India}
	{Chandigarh, India}
	{May 2017 – Jul 2017}
	{\begin{cvitems}
		\item {Worked with software testing team to provide client feedback and troubleshooting for the DgSecure.}
		\item {Continous manual testing of the DgSecure product to ensure the Quality.}
		\item {Automated DgSecure Connection Managment Module using Selenium/Python.}
		\end{cvitems}}
\end{cventries}
\cvsection{Skill Set}
\begin{cventries}
	\cventry
	{}
	{\def\arraystretch{1.15}{\begin{tabular}{ l l }
		Programming:  & {\skill{ C, C++, Python, HTML/CSS, JavaScript}} \\
		DevOps:  & {\skill{ AWS EC2, OpenStack}} \\
		Framework:  & {\skill{ Bootstrap, Selenium}} \\
		Design Tools:  & {\skill{ Adobe PhotoShop}} \\
		\end{tabular}}}
	{}
	{}
	{}
\end{cventries}

\vspace{-7mm}
\cvsection{Projects}
\begin{cventries}
	\cventry
	{MediGo - Platform for medicine delivery at door step. Person can upload his prescription and the medicine will be recommended based on the prescription. Also there is a database connection for the website.}
	{MediGo - Medicine Delivery Website Using Php and MySQL}
	{HTML/CSS, JavaScript, PhP, MySQL}
	{}
	{}
	
	\vspace{-5mm}
	\cventry
	{This project includes implementation of Bully Election Algorithm and Token Ring Election Algorithm for Distributed System with N nodes. Programming language used is C.}
	{Implementing Election algorithm for Distributed System with N nodes}
	{C}
	{}
	{}
	
	\vspace{-5mm}
	\cventry
	{Full Stack Developer at RCI Transports and Logistics. From Front End to Back End and in between. Deployed SMS notification System also at admin site to notify the customer for the delivery of product.}
	{Rajdhani Corporation India Website}
	{HTML/CSS, JQuery, JavaScript, PhP}
	{http://www.rajdhanicorporation.com/}
	{}
	
	\vspace{-5mm}
	\cventry
	{Implementing file transfer socket in UNIX environment. Based on the file size bandwidth utilization was carried out. Network analysis was made using Wireshark. Research Paper is accepted for this under ICCSP\textquotesingle{}18}
	{Bandwidth Analysis of File Transfer Protocol ICCSP\textquotesingle{}18}
	{C, WireShark}
	{}
	{}
	
	\vspace{-5mm}
\end{cventries}
\cvsection{Interests}
\begin{cvhonors}
	\cvhonor
	{PhotoGraphy}
	{}
	{}
	{}
	\cvhonor
	{Cooking}
	{}
	{}
	{}
\end{cvhonors}
\ 
\end{document}
